% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Peng Liu}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Staff Recruiter \\
%Senior Staff Recruiter \\
Broadcom Corporation\\
5300 California Avenue\\
Irvine, California 92617}

\begin{center}
\large\bf PENG LIU\\
111 South Busey Avenue \\ Urbana, IL 61801 \\ (217) 898-3636
\end{center} 
%\vfill % forces letterhead to top of page

\opening{Dear Sir/Madam:}
 
\noindent I'm writing to you because I'm interested in applying 
for the position as Software Engineer in your esteemed company. 

\noindent In my most recent project, I'm right working on power management. I have created a set of methods to analyze and optimize the energy usage, as well as implemented necessary functions in Linux kernel device applications and host machine. This is the unique way Motorola Mobility development team used to analyze energy perform ace. The energy performance is one of the most important and complicated topic for embedded system. It involves almost all aspects of embedded system, from hardware to software. I'll be glad if I can have a chance to share my knowledge in your team. 

\noindent Working for 7 years in the embedded software industry as a developer, I would say I understand the job in a insight way and I am fit in the requirements very well. Being familiar with advanced debugging tools and profiling would help a lot in system level support. For the last several years of my career, I have been focusing on the debug techniques, especially for Android and Embedded Linux. A systematic solution of capturing logs and system snapshots for debug purpose which I proposed and led the development of, has been widely used in all Motorola Mobility products.

\noindent Thank you for reading. I'm looking forward to hearing from you soon. I'll appreciate it if we can have a change to talk in person. 
 
\closing{Sincerely yours,}
 
 
\encl{}  				% Enclosures

\end{letter}
 

\end{document}




