% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{LIU, PENG}
% \address used twice to have two lines of address
\address{111 South Busey Avenue Apt 5, Urbana, IL 61801}
\address{(217)898-3636\\
  pengliu2@illinois.edu}
 
\begin{resume}
 
\section{OBJECTIVE} Looking for a position as a software engineer where I can utilize my skills in Linux programming and experiences in embedded device development to be a valuable team player in your organization. 
 
\section{COMPUTER \\ SKILLS} {\sl Languages:} C, ARM assembly, Python, Java, Perl, PowerPC Assembly

                {\sl Platforms \& SDKs:} Linux, Android, Qt, Hopen OS, WDM SDK, Eclipse, NI-DAQmx
                
                {\sl Software:} Git, Clearcase, Foswiki, Mercurial
 
                \section{EXPERIENCE} {\sl Senior Software Engineer} \hfill Feb 2006 - Present \\
                Motorola, Libertyville, IL and Beijing, China

                \begin{itemize}  %\itemsep -2pt % reduce space between items
                \item Developing tools with C, Python, Perl and Java to implement power management
                  features and improve their performance for Android on OMAP platform.
                \item Developed software features with C and assembly in user space and kernel space
                  to enable native application and kernel debugging for Android on OMAP platform.
                \item Developed a tool to debug issues in MPU-modem communication.
                \item Leading a 5-member team, developed a software integration tool, 
                  an Eclipse-based application, for Motorola iDEN product line. The tool 
                  was used in daily work of over 400 developers worldwide.
                \end{itemize}
 
                {\sl Software Engineer} \hfill                  Aug 2003 - Jan 2006 \\
                Pollex Mobile Software Co.(Mobile Product
                Unit of Hopen Software Engineering Co. before 2005), Beijing, China

                 \begin{itemize}  %\itemsep -2pt %reduce space between items
                 \item Developed part of interrupt handling subsystem and block device
                   subsystem of Hopen Operating System 3.0, which was certificated as one of best
                   innovative products by Beijing Municipal Science and Technology Committee.
                 \item Deployed Hopen Operating System in different machines. Major work included
                   extending the platform-dependent layer of Hopen OS to support IBM PowerPC 405
                   core as well as Intel XScale Wireless MMX technology, and developing device
                   drivers such as the LCD controller and the USB controller of more than 5 mobile
                   products of Lenovo, NEC and Haier.
                 \item Developed prototyping projects with multiple emerging software frameworks
                   for mobile products, such as Qtopia and OpenMoko, and submitted evaluation 
                   reports to management team.
                 \end{itemize}
                {\sl Research Assistant} \hfill                 Sep 2000 - Jul 2003 \\
                State Key Lab of Fire Science, Hefei, China

                  \begin{itemize}
                  \item Participated in the research project, the application of Ethernet in real-time
                    control system. 
                   \item As a programmer, participated in the project to construct a ceramics
                     manufacture control system, designed and implemented a CAN field bus interface
                     circuit board and its WDM driver.
                   \end{itemize} 
 
\section{EDUCATION} {\sl}
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                M.C.S. ONLINE in Computer Science \hfill Present\\
                University of Illinois, Urbana, IL

                M.E. in Safety Engineering \hfill 2000-2003\\
                University of Science and Technology of China, Hefei, China

                B.E. in Automation \hfill 1995-2000\\
                University of Science and Technology of China, Hefei, China
 
\section{ACTIVITIES}             
                Captain of the college basketball team of USTC\\
                Member of the track and field team of Nankai High School

\end{resume}
\end{document}

