% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Peng Liu}
% \address used twice to have two lines of address
\address{111 South Busey Avenue, Urbana, IL 61801}
\address{(217) 898-3636}

 
\begin{resume}
 
\section{OBJECTIVE} Position as Software Engineer.
 
\section{EDUCATION} {\sl}
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                M.C.S. in Computer Science\\
                University of Illinois, Urbana, IL, present

                M.E. in Safety Engineering\\
                University of Science and Technology of China, Hefei, China, 2000-2003

                B.E. in Automation\\
                University of Science and Technology of China, Hefei, China, 1995-2000
 
\section{COMPUTER \\ SKILLS} {\sl Languages:} C, ARM assembly, Python, Java, Perl, PowerPC Assembly\\
                {\sl Platforms \& SDKs:} Linux, Android, Qt, Hopen OS, WDM SDK
                {\sl Software:} Git, Clearcase, Foswiki
 
                \section{EXPERIENCE} {\sl Senior Software Engineer} \hfill Feb 2006 - Present \\
                Motorola, Libertyville, IL and Beijing, China
                \begin{itemize}  \itemsep -2pt % reduce space between items
                \item Developing tools for Android on OMAP platform to implement power management
                  features and improve their performance.
                \item Developed software features to enable native application and kernel debugging
                  for Android on OMAP platform.
                \item Developed tools to debug issues of MPU-modem communication.
                \item As head of 5-member team to develop a software integration tool, 
                  an Eclipse-based application, for Motorola iDEN product line. The tool 
                  was used in daily work of over 400 developers worldwide.
                \end{itemize}
 
                {\sl Software Engineer} \hfill                  Aug 2003 - Jan 2006 \\
                Pollex Mobile Software Co.(Mobile Product
                Unit of Hopen Software Engineering Co. before 2005), Beijing, China
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item As a key contributor, developed interrupt handling subsystem and block device
                   subsystem of Hopen Operating System 3.0, which was certificated as one of best
                   innovative products by Beijing Municipal Science and Technology Committee.
                 \item Deployed Hopen Operating System in different machines. Major work included
                   extending the platform-dependent layer of Hopen OS to support IBM PowerPC 405
                   core as well as Intel XScale Wireless MMX technology, and developing device
                   drivers such as the LCD controller and the USB controller of more than 5 mobile
                   products of Lenovo, NEC and Haier.
                 \item Developed prototyping projects with multiple emerging software frameworks
                   for mobile products, such as Qtopia and OpenMoko, and submitted evaluation 
                   reports to management team.
                 \end{itemize}
                {\sl Research Assistant} \hfill                 Sep 2000 - Jul 2003 \\
                State Key Lab of Fire Science, Hefei, China
                  \begin{itemize}
                  \item Participated in the research project, the application of Ethernet in real-time
                    control system. 
                   \item As a programmer, participated in the project to construct a ceramics
                     manufacture control system, designed and implemented a CAN field bus interface
                     circuit board and its WDM driver.
                   \end{itemize} 
 
\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
                College basketball team of USTC\\
                Track and field team of Nankai High School

\end{resume}
\end{document}







